### 2025-04-07 download-football-data.qmd
20250407 - updates

@@

```{r}
nfl_participation_raw <- progressr::with_progress(
  nflreadr::load_participation(
    seasons = TRUE,
    include_pbp = TRUE))
```

@@

>>>>

Now, let's identify the unique seasons of play-by-play data for use in later calculations:

```{r}
seasons <- unique(nfl_pbp$season)
```

@@

```{r}
nfl_participation_raw <- progressr::with_progress(
  nflreadr::load_participation(
    seasons = 2016:2023, # participation data are no longer available after 2023
    include_pbp = TRUE))
```

@@

We set the `seasons` variable in @sec-downloadPlayByPlay.
